---
title: 14 Data Science Projects
author: E-Zhen Tan
date: '2020-09-24'
slug: 14-data-science-projects
categories: []
tags: []
---

<style>
body {
text-align: justify;
font-size: 16px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
```

```{r install_packages, include=FALSE}
r = getOption("repos")
r["CRAN"] = "http://cran.us.r-project.org"
options(repos = r)

#install.packages('plotly')
library(plotly)

library(dplyr)
library(readr)
```

```{r last_edited, eval=TRUE}
last_edited <- format(Sys.time(), '%Y-%m-%d')
cat('Last edited on', last_edited)
```

This post serves as a documentation of 14 Data Science projects I am committing to complete. Why am I doing this? Recently, I came across a video by Thomas Frank (from College Info Geek) about [the 1% Rule](https://www.youtube.com/watch?v=t_FSSC-ixK8), and it really got me thinking. In essence, the 1% rule states that with every new project or work, there should be an improvement of 1%. This may seem small, but with time and with more projects, it will not take long for the progress to increase exponentially.

As such, I decided to embark on a series of projects that I can do to kickstart the consistency that I would need to truly capitalize on the 1% rule. For this post, I have followed the project ideas from Terence S's (2020) post, *14 Data Science Projects to do During Your 14 Day Quarantine*, linked [here](https://towardsdatascience.com/14-data-science-projects-to-do-during-your-14-day-quarantine-8bd60d1e55e1). The projects consist of 3 Visualization, 6 Exploratory Data Analysis, 5 Predictive Modelling projects.

With this post, I aim to upload my outputs here, and list my learning points and/or improvements after each project. Additionally, all outputs will be from code, unless otherwise stated (when I have produced the outputs in Tableau).

***

## Project 1: [Visualization] Coronavirus and the Global Spread Over Time

*Date completed: 2020-09-24*\

Learning points:

* Using Plotly for the first time in Python, and converting the code to be used in R
* Data Frame manipulation in R

Area(s) to work on: 

* Creating an interactive chart with sliders in R to show the spread of the coronavirus over time. Managed to do it in Python with Plotly Express, but this is not available in R.


```{r read_Data, eval=TRUE}
# Import data
df <- read_csv('covid_19_data.csv', col_types='dccccddd')

# Rename columns
df <- rename(df, Country='Country/Region', Date=ObservationDate)

# Manipulate dataframe
df_countries <- df %>%
  group_by(Country, Date) %>%
  summarise(Confirmed = sum(Confirmed))

df_countries <- arrange(df_countries, desc(Date))
df_countries <- distinct(df_countries, Country, .keep_all=TRUE)
df_countries <- filter(df_countries, Confirmed > 0)

g <- list(showframe=FALSE,
          showcoastlines=FALSE,
          projection=list(type='equirectangular'))

fig <- plot_ly(df_countries, type='choropleth', locations=df_countries$Country, 
               locationmode='country names',
               z=df_countries$Confirmed, colorscale='Reds',
               marker=list(line=list(color='black', width=0.5)))

fig <- fig %>% 
  layout(title=list(text='Confirmed Cases as of September 23, 2020')) %>%
  layout(geo=g)

fig
```

```{r interactive_chart, include=FALSE, eval=FALSE}
df_countrydate <- filter(df, Confirmed > 0)
df_countrydate <- df_countrydate %>%
  group_by(Date, Country) %>%
  summarise(Confirmed=sum(Confirmed))

g_2 <- list(showframe=FALSE,
            showcoastlines=FALSE)

fig_2 <- plot_ly(df_countrydate, type='choropleth', locations=df_countrydate$Country, 
                 locationmode='country names', color=df_countrydate$Confirmed,
                 hover_name=df_countrydate$Country, animation_frame=df_countrydate$Date)

fig_2 <- fig_2 %>% 
  layout(title=list(text='Global Spread of Coronavirus')) %>%
  layout(geo=g_2)

fig_2
```

***

## References

1. Frank, Thomas (n.d.). My 1% Rule Journal. Retrieved from: https://thomasjfrank.com/my-1-rule-journal/

2. S, Terence (2020, April 5). 14 Data Science Projects to do During Your 14 Day Quarantine. *Towards Data Science*. Retrieved from: https://towardsdatascience.com/14-data-science-projects-to-do-during-your-14-day-quarantine-8bd60d1e55e1

